% ---------
%  Compile with "pdflatex hw4".
% --------
%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article}
\usepackage{jeffe,handout,graphicx}
\usepackage[utf8]{inputenc}		% Allow some non-ASCII Unicode in source

%  Redefine suits
\usepackage{pifont}
\def\Spade{\text{\ding{171}}}
\def\Heart{\text{\textcolor{Red}{\ding{170}}}}
\def\Diamond{\text{\textcolor{Red}{\ding{169}}}}
\def\Club{\text{\ding{168}}}

\def\Cdot{\mathbin{\text{\normalfont \textbullet}}}
\def\Sym#1{\textbf{\texttt{\color{BrickRed}#1}}}



% =====================================================
%   Define common stuff for solution headers
% =====================================================
\Class{CS/ECE $374$}
\Semester{FALL $2018$}
\Authors{3}
\AuthorOne{Zhe Zhang}{zzhan157@illinois.edu}
\AuthorTwo{Ray Ying}{xinruiy2@illinois.edu}
\AuthorThree{Anqi Yao}{anqiyao2@illinois.edu}
%\Section{}
% =====================================================
\documentclass[12pt]{article}
\usepackage{tikz}
\begin{document}

% ---------------------------------------------------------

\HomeworkHeader{$9$}{$2$}
\item Define a TM generator (or enumerator) $G$ as a TM with a single
  work tape, but also a special write-only output tape that starts
  with $\#$ at the left most cell, and the write head one cell to the
  right of that.  Assume for simplicity that the input alphabet is
  binary.  From time to time, depending on its computation on the work
  tape, the generator may write a character on the output tape and
  move the output head to the right.  It is said to generate a word
  $w$ if at some point in time, $\#w\#$ is on the output tape. The
  language generated by $G$, denoted by $L(G)$, is the set of all
  strings that $G$ ever generates.
  \begin{itemize}
  \item A generator $G$ is well-behaved if the strings it generates
    are lexicographically ordered. Prove that a language $L$ is
    recursive if and only if there is a well-behaved generator $G$ such
    that $L=L(G)$. Note that you need
    to show both directions separately. {\em Hint:} Treat the case of finite and
    infinite languages separately.

  \item Prove that a language $L$ is recursively enumerable if and
    only if $L = L(G)$ for some TM generator $G$. Note that you need
    to show both directions separately. {\em Hint:} Use the idea of
    dovetailing.
  \end{itemize}
  In proving the statement it suffices to show a construction. We
  describe one case. Suppose you want to show that $L$ is recursively
  enumerable implies that there is a generator $G$ such that
  $L = L(G)$. In order to prove this you need to come up with an
  algorithm that uses, as its input, a description/code
  $\langle M \rangle$ of a TM $M$ and outputs the description/code
  $\langle G \rangle$ of generator TM $G$ such that $L(G) = L(M)$.  You
  do not have to actually prove the correctness of your algorithm as long as
  the description is clear.

\hrule


\begin{solution}


\end{solution}
\end{document}