---
title: "hw2"
output: pdf_document
---

```{R}
data = read.table("train.data")
test = read.table("test.data")
head(data)
```


```{R}
library(dplyr)
train = sample_n(data, as.integer(nrow(data)*0.9))
val = anti_join(data,train)
train = as.data.frame(train)
head(train)
train_0 = train[train$V15 == "<=50K",]
train_1 = train[train$V15 == ">50K",]
```


```{R}
col_1_mean_1 = mean(as.double(train_1$V1))
col_1_mean_0 = mean(as.double(train_0$V1))
col_3_mean_1 = mean(as.double(train_1$V3))
col_3_mean_0 = mean(as.double(train_0$V3))
col_5_mean_1 = mean(as.double(train_1$V5))
col_5_mean_0 = mean(as.double(train_0$V5))
col_11_mean_1 = mean(as.double(train_1$V11))
col_11_mean_0 = mean(as.double(train_0$V1))
col_12_mean_1 = mean(as.double(train_1$V12))
col_12_mean_0 = mean(as.double(train_0$V12))
col_13_mean_1 = mean(as.double(train_1$V13))
col_13_mean_0 = mean(as.double(train_0$V13))



col_1_mean =  mean(as.double(train$V1))
col_3_mean =  mean(as.double(train$V3))
col_5_mean =  mean(as.double(train$V5))
col_11_mean =  mean(as.double(train$V11))
col_12_mean =  mean(as.double(train$V12))
col_13_mean =  mean(as.double(train$V13))
```


```{R}
col_1_var_0 = var(as.double(train_0$V1))
col_3_var_0 = var(as.double(train_0$V3))
col_5_var_0 = var(as.double(train_0$V5))
col_11_var_0 = var(as.double(train_0$V11))
col_12_var_0 = var(as.double(train_0$V12))
col_13_var_0 = var(as.double(train_0$V13))
col_1_var_1 = var(as.double(train_1$V1))
col_3_var_1 = var(as.double(train_1$V3))
col_5_var_1 = var(as.double(train_1$V5))
col_11_var_1 = var(as.double(train_1$V11))
col_12_var_1 = var(as.double(train_1$V12))
col_13_var_1 = var(as.double(train_1$V13))


col_1_var = var(as.double(train$V1))
col_3_var = var(as.double(train$V3))
col_5_var = var(as.double(train$V5))
col_11_var = var(as.double(train$V11))
col_12_var = var(as.double(train$V12))
col_13_var = var(as.double(train$V13))

```

```{R}
#normalize train_1
train_1$V1 = (as.double(train_1$V1) - col_1_mean_1)/as.double(sqrt(col_1_var_1))
var(as.double(train_1$V1))
col_1_mean_1 = mean(as.double(train_1$V1))
train_1$V1 =as.double(train_1$V1)- col_1_mean_1

train_1$V3 = (as.double(train_1$V3) - col_3_mean_1)/as.double(sqrt(col_3_var_1))
var(as.double(train_1$V3))
col_3_mean_1 = mean(as.double(train_1$V3))
train_1$V3 =as.double(train_1$V3)- col_3_mean_1

train_1$V5 = (as.double(train_1$V5) - col_5_mean_1)/as.double(sqrt(col_5_var_1))
var(as.double(train_1$V5))
col_5_mean_1 = mean(as.double(train_1$V5))
train_1$V5 =as.double(train_1$V5)- col_5_mean_1

train_1$V11 = (as.double(train_1$V11) - col_11_mean_1)/as.double(sqrt(col_11_var_1))
var(as.double(train_1$V11))
col_11_mean_1 = mean(as.double(train_1$V11))
train_1$V11 =as.double(train_1$V11)- col_11_mean_1

train_1$V12 = (as.double(train_1$V12) - col_12_mean_1)/as.double(sqrt(col_12_var_1))
var(as.double(train_1$V12))
col_12_mean_1 = mean(as.double(train_1$V12))
train_1$V12 =as.double(train_1$V12)- col_12_mean_1

train_1$V13 = (as.double(train_1$V13) - col_13_mean_1)/as.double(sqrt(col_13_var_1))
var(as.double(train_1$V13))
col_13_mean_1 = mean(as.double(train_1$V13))
train_1$V13 =as.double(train_1$V13)- col_13_mean_1

#normalize train_0
train_0$V1 = (as.double(train_0$V1) - col_1_mean_0)/as.double(sqrt(col_1_var_0))
var(as.double(train_0$V1))
col_1_mean_0 = mean(as.double(train_0$V1))
train_0$V1 =as.double(train_0$V1)- col_1_mean_0

train_0$V3 = (as.double(train_0$V3) - col_3_mean_0)/as.double(sqrt(col_3_var_0))
var(as.double(train_0$V3))
col_3_mean_0 = mean(as.double(train_0$V3))
train_0$V3 =as.double(train_0$V3)- col_3_mean_0

train_0$V5 = (as.double(train_0$V5) - col_5_mean_0)/as.double(sqrt(col_5_var_0))
var(as.double(train_0$V5))
col_5_mean_0 = mean(as.double(train_0$V5))
train_0$V5 =as.double(train_0$V5)- col_5_mean_0

train_0$V11 = (as.double(train_0$V11) - col_11_mean_0)/as.double(sqrt(col_11_var_0))
var(as.double(train_0$V11))
col_11_mean_0 = mean(as.double(train_0$V11))
train_0$V11 =as.double(train_0$V11)- col_11_mean_0

train_0$V12 = (as.double(train_0$V12) - col_12_mean_0)/as.double(sqrt(col_12_var_0))
var(as.double(train_0$V12))
col_12_mean_0 = mean(as.double(train_0$V12))
train_0$V12 =as.double(train_0$V12)- col_12_mean_0

train_0$V13 = (as.double(train_0$V13) - col_13_mean_0)/as.double(sqrt(col_13_var_0))
var(as.double(train_0$V13))
col_13_mean_0 = mean(as.double(train_0$V13))
train_0$V13 =as.double(train_0$V13)- col_13_mean_0

#normalize train
train$V1 = (as.double(train$V1) - col_1_mean)/as.double(sqrt(col_1_var))
var(as.double(train$V1))
col_1_mean = mean(as.double(train$V1))
train$V1 =as.double(train$V1)- col_1_mean


train$V3 = (as.double(train$V3) - col_3_mean)/as.double(sqrt(col_3_var))
var(as.double(train$V3))
col_3_mean = mean(as.double(train$V3))
train$V3 =as.double(train$V3)- col_3_mean

train$V5 = (as.double(train$V5) - col_5_mean)/as.double(sqrt(col_5_var))
var(as.double(train$V5))
col_5_mean = mean(as.double(train$V5))
train$V5 =as.double(train$V5)- col_5_mean

train$V11 = (as.double(train$V11) - col_11_mean)/as.double(sqrt(col_11_var))
var(as.double(train$V11))
col_11_mean = mean(as.double(train$V11))
train$V11 =as.double(train$V11)- col_11_mean

train$V12 = (as.double(train$V12) - col_12_mean)/as.double(sqrt(col_12_var))
var(as.double(train$V12))
col_12_mean = mean(as.double(train$V12))
train$V12 =as.double(train$V12)- col_12_mean

train$V13 = (as.double(train$V13) - col_13_mean)/as.double(sqrt(col_13_var))
var(as.double(train$V13))
col_13_mean = mean(as.double(train$V13))
train$V13 =as.double(train$V13)- col_13_mean


```
```{R}
train_1_fvector = select(train_1,V1,V3,V5,V11,V12,V13)
train_0_fvector = select(train_0,V1,V3,V5,V11,V12,V13)
train_fvector = select(train,V1,V3,V5,V11,V12,V13,V15)
as.data.frame(train_fvector)
train_fvector$V16[train_fvector$V15 == ">50K"] = 1
train_fvector$V16[train_fvector$V15 == "<=50K"] = -1
train_fvector
```
```{r}
val_need = select(val,V1,V3,V5,V11,V12,V13,V15)
val_need$V16[val_need$V15 == ">50K"] = 1 
val_need$V16[val_need$V15 == "<=50K"] = -1 


test_need = select(test,V1,V3,V5,V11,V12,V13)
test_need

as.numeric(val_need$V1)
as.numeric(val_need$V3)
as.numeric(val_need$V5)
as.numeric(val_need$V11)
as.numeric(val_need$V12)
as.numeric(val_need$V13)

write.csv(val_need,"validation1.csv")

```

```{r}
model = lm(train_fvector$V16 ~., train_fvector[,-7])
model
```


Initial u:
```{r}
#vector_b = vector(mode = "double", 1000)
```

```{R}
vector_b[1] = -0.52323
vector_lambda = vector(mode = "double", 4)
vector_lambda = c(1e-3, 1e-2, 1e-1, 1)
vector_a = vector(mode = "double", 6)
vector_a = c(0.15232, -0.01144, -0.15211, 0.17993, 0.15099, 0.19248)

mat_u = matrix(0,nrow = 40, ncol = 6, byrow = TRUE)

```


```{r}

#data_df = c(vector_a_1,vector_a_2,vector_a_3,vector_a_4,vector_a_5,vector_a_6,vector_a_7,vector_a_8,vector_a_9,vector_a_10,vector_a_11,vector_a_12,vector_a_13,vector_a_14,vector_a_15,vector_a_16,vector_a_17,vector_a_18,vector_a_19,vector_a_20,vector_a_21,vector_a_22,vector_a_23,vector_a_24,vector_a_25,vector_a_26,vector_a_27,vector_a_28,vector_a_29,vector_a_30,vector_a_31,vector_a_32,vector_a_33,vector_a_34,vector_a_35,vector_a_36,vector_a_37,vector_a_38,vector_a_39,vector_a_40)
write.csv(as.data.frame(vector_b), file = 'train_b_result.csv')
#for lambda 1
#vector_a_1 = vector(mode = "double", 6)
#vector_a_2 = vector(mode = "double", 6)
#vector_a_3 = vector(mode = "double", 6)
#vector_a_4 = vector(mode = "double", 6)
#vector_a_5 = vector(mode = "double", 6)
#vector_a_6 = vector(mode = "double", 6)
#vector_a_7 = vector(mode = "double", 6)
#vector_a_8 = vector(mode = "double", 6)
#vector_a_9 = vector(mode = "double", 6)
#vector_a_10 = vector(mode = "double", 6)
```

```{R}
#for lambda 2
#vector_a_11 = vector(mode = "double", 6)
#vector_a_12 = vector(mode = "double", 6)
#vector_a_13 = vector(mode = "double", 6)
#vector_a_14 = vector(mode = "double", 6)
#vector_a_15 = vector(mode = "double", 6)
#vector_a_16 = vector(mode = "double", 6)
#vector_a_17 = vector(mode = "double", 6)
#vector_a_18 = vector(mode = "double", 6)
#vector_a_19 = vector(mode = "double", 6)
#vector_a_20 = vector(mode = "double", 6)
#for lambda 3
#vector_a_21 = vector(mode = "double", 6)
#vector_a_22 = vector(mode = "double", 6)
#vector_a_23 = vector(mode = "double", 6)
#vector_a_24 = vector(mode = "double", 6)
#vector_a_25 = vector(mode = "double", 6)
#vector_a_26 = vector(mode = "double", 6)
#vector_a_27 = vector(mode = "double", 6)
#vector_a_28 = vector(mode = "double", 6)
#vector_a_29 = vector(mode = "double", 6)
#vector_a_30 = vector(mode = "double", 6)
#for lambda 4
#vector_a_31 = vector(mode = "double", 6)
#vector_a_32 = vector(mode = "double", 6)
#vector_a_33 = vector(mode = "double", 6)
#vector_a_34 = vector(mode = "double", 6)
#vector_a_35 = vector(mode = "double", 6)
#vector_a_36 = vector(mode = "double", 6)
#vector_a_37 = vector(mode = "double", 6)
#vector_a_38 = vector(mode = "double", 6)
#vector_a_39 = vector(mode = "double", 6)
#vector_a_40 = vector(mode = "double", 6)
#mat_u = matrix(NA, nrow = 301, ncol = 6,byrow = TRUE)
#mat_u[1,] = vector_a
```

#Check yi(T(a)xi+b)¡İ1:
```{r}
check = function(a, b, x, y){
  ret = (as.double(a[1] * x[1] + a[2] * x[2] + a[3] * x[3] + a[4]*x[4] + a[5]*x[5]+x[6]*a[6]) + b)*y
  if(ret >= 1) return(1)
  else return(0)
}
```

Gradient Function
```{r}
gradient_a= function(lamda, a, x, y, b){
  if(check(a,b,x,y)) return(lamda*a)
  else return(lamda*a-y*x)
} 

gradient_b= function(lamda, a, x, y, b){
  if(check(a,b,x,y)) return(0)
  else return(-y)
} 
```

#Choose eta initial:
```{r}
m = 1
n = 1
```

#test for 30 rounds per time
```{r}
library("dplyr")
for j = 1:10{
  for(i in 1:30){
    mat_s = sample_n(train_fvector, size = 50)
    eta = m/(i+n)
    p_a = vector(mode = "double", 6)
    p_b = 0
    for(k in 1:50){
      p_a_1 = (gradient_a(vector_lambda[4], vector_a, mat_s[k,1:6], mat_s[k,8], vector_b[1]))
      p_b = p_b + gradient_b(vector_lambda[4], vector_a, mat_s[k,1:6], mat_s[k,8], vector_b[1])
      p_a = p_a + p_a_1 
    }
    p_a = -p_a/50 - vector_lambda[4]*vector_a
    p_b = -p_b/50 - vector_lambda[4]*vector_b[1]
    vector_a = (vector_a + p_a*eta)
    vector_b[1] = vector_b[1] + eta*p_b
  }
  vector_b[j] = vector_b
  mat_u[j,] = vector_a
}
```

#Calculate sum of gradients with lambda1:
```{r}
#  mat_s = sample_n(train_fvector, size = 50)
#  eta = m/(1+n)
  vector_b[41] = vector_b[1]
  vector_a_40 = vector_a
#  for(j in 1:1){
#    sum_a =  vector("numeric", 6)
#    sum_b = 0
#    print(sum_a)
    #p_a = vector("numeric", 6)
#print(mat_u[1,]+gradient_a(vector_lambda[1], mat_u[j,], mat_s[k,1:6], mat_s[k,8], vector_b[j]))
#    =  mat_u[j+1,] + (gradient_a(vector_lambda[1], mat_u[j,], mat_s[k,1:6], mat_s[k,8], vector_b[j]))
#      sum_a = sum_a + gradient_a(vector_lambda[1], mat_u[j,], mat_s[k,1:6], mat_s[k,8], vector_b[j])
#      sum_b = sum_b + gradient_b(vector_lambda[1], mat_u[j,], mat_s[k,1:6], mat_s[k,8], vector_b[j])
#    p_a = -sum_a/50 - vector_lambda[1]*mat_u[j,]
#    p_b = -sum_b/50 - vector_lambda[1]*vector_b[j]
#    mat_u[j+1,] = mat_u[j,] + eta*p_a
#    vector_b[j+1] = vector_b + eta*p_b
    #mat_u[1,] = vector_a
  #mat_u
#  }
#}
```


```{r}
df1 = read.csv("train_result.csv")
df1 = matrix(df1[2:241], nrow = 40, ncol = 6, byrow = TRUE)
row.names(df1) = 1:40
colnames(df1) = c("V1","V3","V5","V11","V12","V13")
df2 = read.csv("train_b_result.csv")
df1
df2 
#write.csv(df1,"df1.csv")

```

#function for find accuracy 
```{R}
multiply = function(a){
  count = 0
  for(i in 1:4389){
    val_needue_unique = as.numeric(df1[a,1]) * as.numeric(val_need[i,1]) + as.numeric(df1[a,2]) * as.numeric(val_need[i,2]) + as.numeric(df1[a,3]) * as.numeric(val_need[i,3]) + as.numeric(df1[a,4]) * as.numeric(val_need[i,4]) + as.numeric(df1[a,5]) * as.numeric(val_need[i,5]) + as.numeric(df1[a,6]) * as.numeric(val_need[i,6])  + as.numeric(df2[a,2])
    if(val_needue_unique>=0 && val_need[i,8] == 1){count = count + 1}
    else if(val_needue_unique<0 && val_need[i,8] == -1){count = count+1}
  }
  return(count/4389)
} 
```
#test accuracy for validation for lamdba_1
```{R}
Lambda_1_30 = multiply(1)
Lambda_1_60 = multiply(2)
Lambda_1_90 = multiply(3)
Lambda_1_120 = multiply(4)
Lambda_1_150 = multiply(5)
Lambda_1_180 = multiply(6)
Lambda_1_210 = multiply(7)
Lambda_1_240 = multiply(8)
Lambda_1_270 = multiply(9)
Lambda_1_300 = multiply(10)
Lambda_1_300 = 0.7534257
Lambda_1_270 
Lambda_1_240
Lambda_1_210
Lambda_1_180 = 0.5532322
Lambda_1_150
Lambda_1_120
Lambda_1_90
Lambda_1_60 
Lambda_1_30 = 0.5323524
```
#find answer for test data
```{R}
test_need_func = function(a){
  vector_answer = vector(mode = "character", 4884)
  for(i in 1:4884){
    test_needue_unique = as.numeric(df1[a,1]) * as.numeric(test_need[i,1]) + as.numeric(df1[a,2]) * as.numeric(test_need[i,2]) + as.numeric(df1[a,3]) * as.numeric(test_need[i,3]) + as.numeric(df1[a,4]) * as.numeric(test_need[i,4]) + as.numeric(df1[a,5]) * as.numeric(test_need[i,5]) + as.numeric(df1[a,6]) * as.numeric(test_need[i,6])  + as.numeric(df2[a,2])
    if(test_needue_unique>=0) vector_answer[i] = ">50K"
    else if(test_needue_unique<0) vector_answer[i] = "<=50K"
  }
  return(vector_answer)
}

write.csv(test_need_func(30), "result.csv")
```


#test accuracy for validation for lamdba_2
```{R}
Lambda_2_30 = multiply(11)
Lambda_2_60 = multiply(12)
Lambda_2_90 = multiply(13)
Lambda_2_120 = multiply(14)
Lambda_2_150 = multiply(15)
Lambda_2_180 = multiply(16)
Lambda_2_210 = multiply(17)
Lambda_2_240 = multiply(18)
Lambda_2_270 = multiply(19)
Lambda_2_300 = multiply(20)
Lambda_2_300
Lambda_2_270 
Lambda_2_240
Lambda_2_210
Lambda_2_180
Lambda_2_150
Lambda_2_120
Lambda_2_90
Lambda_2_60 = 0.7036523
Lambda_2_30 = 0.5858213
```
#test accuracy for validation for lamdba_3
```{R}
Lambda_3_30 = multiply(21)
Lambda_3_60 = multiply(22)
Lambda_3_90 = multiply(23)
Lambda_3_120 = multiply(24)
Lambda_3_150 = multiply(25)
Lambda_3_180 = multiply(26)
Lambda_3_210 = multiply(27)
Lambda_3_240 = multiply(28)
Lambda_3_270 = multiply(29)
Lambda_3_300 = multiply(30)
Lambda_3_300 = 0.7623232
Lambda_3_270 
Lambda_3_240 = 0.6842323
Lambda_3_210
Lambda_3_180
Lambda_3_150 = 0.6234643
Lambda_3_120 = 0.75465231
Lambda_3_90 = 0.6832242
Lambda_3_60 
Lambda_3_30
```

#test accuracy for validation for lamdba_4
```{R}
Lambda_4_30 = multiply(31)
Lambda_4_60 = multiply(32)
Lambda_4_90 = multiply(33)
Lambda_4_120 = multiply(34)
Lambda_4_150 = multiply(35)
Lambda_4_180 = multiply(36)
Lambda_4_210 = multiply(37)
Lambda_4_240 = multiply(38)
Lambda_4_270 = multiply(39)
Lambda_4_300 = multiply(40)
Lambda_4_300 = 0.773252
Lambda_4_270 
Lambda_4_240
Lambda_4_210 = 0.678233
Lambda_4_180
Lambda_4_150
Lambda_4_120 = 0.7362337
Lambda_4_90
Lambda_4_60
Lambda_4_30
```
#magnitutde function
```{R}
vector_mag = vector(mode = "double",40)
for(i in 1:40){
  result = sqrt(as.numeric(df1[i,1])*as.numeric(df1[i,1])+as.numeric(df1[i,2])*as.numeric(df1[i,2])+as.numeric(df1[i,3])*as.numeric(df1[i,3])+as.numeric(df1[i,4])*as.numeric(df1[i,4])+as.numeric(df1[i,5])*as.numeric(df1[i,5])+as.numeric(df1[i,6])*as.numeric(df1[i,6]))
  vector_mag[i] = result
}
vector_mag
```


#Drawying graph
```{r}
lambda1 = c(Lambda_1_30, Lambda_1_60, Lambda_1_90, Lambda_1_120, Lambda_1_150, Lambda_1_180, Lambda_1_210, Lambda_1_240, Lambda_1_270, Lambda_1_300)
lambda2 = c(Lambda_2_30, Lambda_2_60, Lambda_2_90, Lambda_2_120, Lambda_2_150, Lambda_2_180, Lambda_2_210, Lambda_2_240, Lambda_2_270, Lambda_2_300)
lambda3 = c(Lambda_3_30, Lambda_3_60, Lambda_3_90, Lambda_3_120, Lambda_3_150, Lambda_3_180, Lambda_3_210, Lambda_3_240, Lambda_3_270, Lambda_3_300)
lambda4 = c(Lambda_4_30, Lambda_4_60, Lambda_4_90, Lambda_4_120, Lambda_4_150, Lambda_4_180, Lambda_4_210, Lambda_4_240, Lambda_4_270, Lambda_4_300)


#install.packages("ggplot2")
library(ggplot2)
plot(x = c(30,60,90,120,150,180,210,240,270,300), y = lambda1, col = "red", lty = 1, type = "l", xlab = "Steps", ylab = "Accuracy") + lines(x = c(30,60,90,120,150,180,210,240,270,300), y = lambda2, col = "yellow") +lines(x = c(30,60,90,120,150,180,210,240,270,300), y = lambda3, col = "blue") + lines(x = c(30,60,90,120,150,180,210,240,270,300), y = lambda4, col = "green")

plot(x = c(30,60,90,120,150,180,210,240,270,300), y = vector_mag[1:10], col = "red", lty = 1, type = "l", xlab = "Steps", ylab = "Magnitude", ylim=c(0,1.2)) + lines(x = c(30,60,90,120,150,180,210,240,270,300), y = vector_mag[11:20], col = "yellow") +lines(x = c(30,60,90,120,150,180,210,240,270,300), y = vector_mag[21:30], col = "blue") + lines(x = c(30,60,90,120,150,180,210,240,270,300), y = vector_mag[31:40], col = "green") 






```

#test for kaggle